DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-09-16 README.Rmd

# DeepTriangle: A Deep Learning Approach to Loss Reserving

This is the companion repository to the DeepTriangle paper. A preprint can be found at [https://arxiv.org/abs/1804.09253](https://arxiv.org/abs/1804.09253).

>>>>

# DeepTriangle

This is the companion repository to the paper [*DeepTriangle: A Deep Learning Approach to Loss Reserving*](https://www.mdpi.com/2227-9091/7/3/97).

### 2019-09-16 manuscript/manuscript.Rmd

[^2]: A portmanteau of *deep learning* and *loss development triangle*

@@

For $l = 1$, we define the previous layer activations as the input, so that the calculation for the first hidden layer becomes
\begin{equation}
h_j^{[1]} = g^{[1]}(w_j^{[1]T}x + b_j^{[1]})
\end{equation}
Also, for the output layer $l = L$, we compute the prediction
\begin{equation}
\hat{y} = h_j^{[L]} = g^{[L]}(w_{j}^{[L]T}h^{[L-1]} + b_j^{[L]}).
\end{equation}

@@

For handling the time series of paid losses and claims outstanding, we utilize gated recurrent units (GRU) [@chung2014empirical], which is a type of recurrent neural network (RNN) building block that is appropriate for sequential data. A graphical representation of a GRU is shown in Figure \ref{fig:gru}, and the associated equations are as follows:

@@

@@

The company code input is first passed to an embedding layer. In this process, each company is mapped to a fixed length vector in $\mathbb{R}^k$, where $k$ is a hyperparameter. In our case, we choose $k = \text{number of levels} - 1 = 49$, as recommended in @DBLP:journals/corr/GuoB16. In other words, each company is represented by a vector in $\mathbb{R}^49$. This mapping mechanism is part of the neural network and hence is learned during the training of the network, instead of in a separate data preprocessing step, so the numerical representations are optimized for predicted the future paid losses. Companies that are similar in the context of our claims forecasting problem are mapped to vectors that are close to each other in terms of Euclidean distance. Intuitively, one can think of this representation as a proxy for characteristics of the companies, such as size of book and case reserving philosophy. Categorical embedding is a common technique in deep learning that has been successfully applied to recommendation systems [@Cheng_2016] and retail sales prediction [@DBLP:journals/corr/GuoB16]. In the actuarial science literature, @richman2018neural utilize embedding layers to capture characteristics of regions in mortality forecasting, while @gabrielli2018neural apply them to lines of business factors in loss reserving.

### Fully connected layers and outputs

Each timestep of the decoded sequence from the GRU decoder is then concatenated with the company embedding output. The concatenated values are then passed to two subnetworks of fully connected layers, each of which shares weights across the timesteps. The two subnetworks correspond to the paid loss and case outstanding predictions, respectively, and each consist of a hidden layer of 64 units with a dropout rate of 0.2, and an output layer of 1 unit to represent a scalar.

@@

is used as the activation function (which we denoted as $g$ in Section \@ref(prelim)) for all fully connected layers, including both of the output layers. We remark that this choice of output activation implies we only predict nonnegative cash flows, i.e. no recoveries. This assumption is reasonable for the dataset we use in our experiments, but may be modified to accommodate other use cases.

@@

[^1]: https://github.com/kasaai/deeptriangle

>>>>

[^2]: A portmanteau of *deep learning* and *loss development triangle*.

@@

For $l = 1$, we define the previous layer activations as the input, so that the calculation for the first hidden layer becomes
\begin{equation}
h_j^{[1]} = g^{[1]}(w_j^{[1]T}x + b_j^{[1]}).
\end{equation}
Also, for the output layer $l = L$, we compute the prediction
\begin{equation}
\hat{y} = h_j^{[L]} = g^{[L]}(w_{j}^{[L]T}h^{[L-1]} + b_j^{[L]}).
\end{equation}

@@

For handling the time series of paid losses and claims outstanding, we utilize gated recurrent units (GRU) [@chung2014empirical], which is a type of recurrent neural network (RNN) building block that is appropriate for sequential data. A graphical representation of a GRU is shown in Figure \ref{fig:gru}, and the associated equations are as follows[^3]:

@@

[^3]: Note the use of angle brackets to index position in a sequence rather than layers in a feedforward neural network as in Section \@ref(prelim).

@@

The company code input is first passed to an embedding layer. In this process, each company is mapped to a fixed length vector in $\mathbb{R}^k$, where $k$ is a hyperparameter. In our case, we choose $k = \text{number of levels} - 1 = 49$, as recommended in @DBLP:journals/corr/GuoB16. In other words, each company is represented by a vector in $\mathbb{R}^{49}$. This mapping mechanism is part of the neural network and hence is learned during the training of the network, instead of in a separate data preprocessing step, so the learned numerical representations are optimized for predicted the future paid losses. Companies that are similar in the context of our claims forecasting problem are mapped to vectors that are close to each other in terms of Euclidean distance. Intuitively, one can think of this representation as a proxy for characteristics of the companies, such as size of book and case reserving philosophy. Categorical embedding is a common technique in deep learning that has been successfully applied to recommendation systems [@Cheng_2016] and retail sales prediction [@DBLP:journals/corr/GuoB16]. In the actuarial science literature, @richman2018neural utilize embedding layers to capture characteristics of regions in mortality forecasting, while @gabrielli2018neural apply them to lines of business factors in loss reserving.

### Fully Connected Layers and Outputs

Each timestep of the decoded sequence from the GRU decoder is then concatenated with the company embedding output. The concatenated values are then passed to two subnetworks of fully connected layers, each of which shares weights across the timesteps. The two subnetworks correspond to the paid loss and case outstanding predictions, respectively, and each consists of a hidden layer of 64 units with a dropout rate of 0.2, followed by an output layer of 1 unit to represent the paid loss or claims outstanding at a time step.

@@

is used as the activation function (which we denote by $g$ in Section \@ref(prelim)) for all fully connected layers, including both of the output layers. We remark that this choice of output activation implies we only predict nonnegative cash flows, i.e. no recoveries. This assumption is reasonable for the dataset we use in our experiments, but may be modified to accommodate other use cases.

@@

[^1]: https://github.com/kasaai/deeptriangle.
